Mash screen results

### 2019-05-06 notebooks/mash_analysis.Rmd
fixed error

# Contaminated Isolates
```{r}
test <- mash_plot_df %>%
  filter(species != "Escherichia coli",
         identity >= 0.95) %>%
  select(id)

@@

test2 <- mash_plot_df %>%
  select(-c(phage,shared_hashes,query_id,query_comment,median_multiplicity,test,p_value)) %>%
  filter(id %in% ids) %>%
  mutate(id2 = 1:n()) %>%
  spread(species, identity, fill = NA) %>%
  select(-id2) %>%
  group_by(id) %>%
  summarise_all(funs(func_paste)) %>%
  mutate(`Escherichia coli` = sapply(`Escherichia coli`, scan_max)) %>%
  mutate_all(funs(gsub("^$", NA, .)))

>>>>

# Contaminated Isolates
```{r, warning=FALSE, message=FALSE}
test <- mash_plot_df %>%
  filter(species != "Escherichia coli",
         identity >= 0.95) %>%
  select(id)

@@

mash_plot_df %>%
  select(-c(phage,shared_hashes,query_id,query_comment,median_multiplicity,test,p_value)) %>%
  filter(id %in% ids) %>%
  mutate(id2 = 1:n()) %>%
  spread(species, identity, fill = NA) %>%
  select(-id2) %>%
  group_by(id) %>%
  summarise_all(funs(func_paste)) %>%
  mutate(`Escherichia coli` = sapply(`Escherichia coli`, scan_max)) %>%
  mutate_all(funs(gsub("^$", NA, .)))
